Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
SR expanded_taken renamed

#Generating sequence rules
SR   <- my_SR(data = sequences   )
SR_PF <- my_SR(data = sequences_PF)
SR_HL <- my_SR(data = sequences_HL)

SR_expanded   <- my_SR(data = sequences_expanded   )
SR_expanded_PF <- my_SR(data = sequences_expanded_PF)
SR_expanded_HL <- my_SR(data = sequences_expanded_HL)
#Saving sequence rules
save(
    SR = SR,
    SR_PF = SR_PF,
    SR_HL = SR_HL,

    SR_expanded    = SR_expanded,
    SR_expanded_PF = SR_expanded_PF,
    SR_expanded_HL = SR_expanded_HL,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL,
   n_students,
   SR, SR_PF, SR_HL,
   SR_expanded, SR_expanded_PF, SR_expanded_HL)

>>>>

#Generating sequence rules
SR_taken   <- my_SR(data = sequences   )
SR_PF      <- my_SR(data = sequences_PF)
SR_HL      <- my_SR(data = sequences_HL)

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)
SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,

    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL,
   n_students,
   SR_taken, SR_PF, SR_HL,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)
